\label{App:Parameter_Est}
Mathematical models for COVID-19 have shown that the
parameters' values are not necessarily the same in each country. We
use COVID-19 data from Mexico City plus Mexico state to follow the
epidemic curve's initial growth in this work. Consequently, we
estimate some parameter values of system in \Cref{model1}
\cite{DataMX}. To obtain the baseline parameter values, we consider
two-stages: i) before and ii) after mitigation measures were
implemented. For both stages, we use model in \Cref{model1} with no
vaccination dynamics ($\lambda_V = 0$ and $V(0) = 0$), and STAN
R-package. This package is used for statistical inference by the
Bayesian approach. For the code implementation of our system, we
follow ideas of \cite{Chatzilena2019}, and it is made freely available
at \cite{gitHub}. For this section, our estimations are focused on
three parameters: $\beta_A$, $\beta_S$ and $p$. Other parameter values
are given in \Cref{table_fixparam}.
\begin{table}[h!]
\begin{center}
	\begin{tabular}{ccc}
		\toprule
		Parameter & Value & References
		\\
		\midrule
		$\delta_{E}^{-1}$ & $5.1\ \text{days}$   &  \cite{Tian2020}
		\\
		$\alpha_{S}^{-1}$  & $5.97\ \text{days}$  &  \cite{Acuna2020}
		\\
		$\alpha_{A}^{-1}$ & $10.81\ \text{days}$ & \cite{Acuna2020}
		\\
		$\delta_{R}^{-1}$ & $365\ \text{days}$     &
		\\
		$\mu^{-1}$        & $70\ \text{years}$   &
		\\
		\bottomrule
		\end{tabular}
		\caption{Fixed parameters values of system in
		\Cref{model1}.}\label{table_fixparam}
	\end{center}
\end{table}

For the first stage, the following system is considered:
\begin{equation}\label{model_stage1}
  \begin{aligned}
	S'(t)&=\mu \bar{N}-\frac{\hat{\beta}_S
	I_S+\hat{\beta}_AI_A}{\bar{N}}S-\mu S + \delta_R R\\
	E'(t)&= \frac{\hat{\beta}_S I_S+\hat{\beta}_A
	I_A}{\bar{N}}S-(\mu+\delta_E) E \\
	I'_S(t)&= p \delta_E E-(\mu+\alpha_S) I_S\\
	I'_A(t)&= (1-p) \delta_E E-(\mu+\alpha_A) I_A \\
	R'(t)&= (1-\theta) \alpha_S I_S+\alpha_A I_A-(\mu+\delta_R) R \\
	D'(t)&= \theta \alpha_S I_S
  \end{aligned}
\end{equation}
where $\bar{N}(t)=S(t)+E(t)+I_S(t)+I_A(t)+R(t)$ and $N=\bar{N}+D$.
Here, we consider COVID-19 data from the first day of symptoms onset
reported (February 19) until March 23, 2020. We also assume that
$\theta = 0$ because the first reported death was on March 18, and
there were three reported deaths until March 23. The initial values of
recovered and dead people are set to zero. Symptomatic class initial
value was fixed in one individual, while $E(0)$ and $I_{A}(0)$ were
estimated. Thus, $S(0) = N - (E(0) + I_{A}(0) + 1)$, where $N =
26446435$ \cite{conavi2020}. For the STAN implementation, we employ a
negative-binomial model as the likelihood function with the mean
parameter given by incidence solution per day. In addition to the
above, we assign prior probability distributions to each parameter and
the exposed and asymptomatic classes' initial conditions. Thus, we
propose that $\hat{\beta}_A$ and $\hat{\beta}_S$ follow a normal
distribution with parameters $\mu = 1$ and $\sigma^2 = 0.13$. Then,
$p$ follows a uniform distribution in $(0, 0.25)$, and $E(0)$ and
$I_{A}(0)$ also follow a uniform distribution in $(2,20)$ and
$(2,10)$, respectively. When employing our STAN implementation, we run
5 chains with 100,500 iterations each, discard the first 500, and use
10,000 samples to generate estimates of parameters $\hat{\beta}_A$,
$\hat{\beta}_S$ and $p$. \Cref{table_icparam} shows the confidence
interval for each parameter and median posterior estimated.
\begin{table}[h!]
\begin{center}
	\begin{tabular}{ccc}
		\toprule
	    Parameter & 95\% Confidence Interval & Quantile 50
			\\
			\midrule
            $\hat{\beta}_S$ & $[0.672, 1.1886]$   &  $0.9322$ \\
            $\hat{\beta}_A$ & $[0.501, 0.7851]$  &  $0.6435$ \\
            $p$       & $[0.061, 0.2206]$ &  $0.1227$ \\
            $R_0$ & $[4.159, 5.1991]$ &  $4.6082$ \\
			\bottomrule
	\end{tabular}
  \caption{Confidence interval and median posterior estimated for some
  parameters of system in \Cref{model_stage1} and basic reproductive
  number $(R_0)$.}\label{table_icparam}
\end{center}
\end{table}

\noindent For the second stage, we took a complete month starting the
day when mitigation measures were implemented, that is, from March 23
to April 23, 2020. Now, we consider parameter $\xi$ to model the
implementation of non-pharmaceutical measures. Thus, system in
\Cref{model_stage1} becomes:
\begin{equation}\label{model_stage2}
  \begin{aligned}
	S'(t)&=\mu \bar{N}-\frac{\xi\hat{\beta}_S
	I_S+\xi\hat{\beta}_AI_A}{\bar{N}}S-\mu S + \delta_R R\\
	E'(t)&= \frac{\xi\hat{\beta}_S
	I_S+\xi\hat{\beta}_AI_A}{\bar{N}}S-(\mu+\delta_E) E \\
	I'_S(t)&= p \delta_E E-(\mu+\alpha_S) I_S\\
	I'_A(t)&= (1-p) \delta_E E-(\mu+\alpha_A) I_A \\
	R'(t)&= (1-\theta) \alpha_S I_S+\alpha_A I_A-(\mu+\delta_R) R \\
	D'(t)&= \theta \alpha_S I_S
  \end{aligned}
\end{equation}
where $\bar{N}(t)=S(t)+E(t)+I_S(t)+I_A(t)+R(t)$ and $N=\bar{N}+D$. At
this stage, we consider that $\theta = 0.11$. Here, our objective is
to estimate the value of parameter $\xi$. To do this, we use the
median posterior of all the estimated parameters from the first stage
(see \Cref{table_icparam}). Other parameter values are given in
\Cref{table_fixparam}. Almost all initial conditions were obtained
when solving system in \Cref{model_stage1} with the 10,000 samples
(obtained in first stage), after which each solution at the final time
(March 23) is saved. We use the median of the saved values. Thus, for
system in \Cref{model_stage2}, $E(0) = 6587.585$, $I_S(0) = 553.7035$,
$I_A(0) = 3149.924$, and $R(0) = 3001.547$. For the initial value of
variable $D$, we consider reported COVID-19 data, then $D(0) = 3$.
Therefore $S(0) = N - (E(0) + I_S(0) + I_A(0) + R(0) + D(0))$, with $N
= 26446435$ \cite{conavi2020}. Similar to the first stage, we consider
a negative-binomial model as the likelihood function with the mean
parameter given by incidence solution per day, while that we postulate
a uniform distribution in $(0.25,0.75)$ as a prior probability
distribution for the parameter $\xi$.
%\label{App:Parameter_Est}
For the second stage, we run 5 chains with 100,500 iterations each,
discard the first 500, and use 10,000 samples to generate estimates of
parameters $\xi$. \Cref{table_icparam2} shows the confidence interval
and median posterior estimated for parameter $\xi$.
\begin{table}[h!]
\begin{center}
	\begin{tabular}{ccc}
		\toprule
	    Parameter & 95\% Confidence Interval & Quantile 50
			\\
			\midrule
            $\xi$     & $[0.3696, 0.4099]$  & $0.3889$  \\
            $R_0$ & $[1.702, 1.887]$ &  $1.791$ \\
			\bottomrule
	\end{tabular}
  \caption{Confidence interval and median posterior estimated for
  parameter $\xi$ of system in \Cref{model_stage2} and basic
  reproductive number $(R_0)$.}\label{table_icparam2}
\end{center}
\end{table}

Finally, it is important to mention that our results were implemented
considering that the effective transmission contact rates
$(\beta_{\bullet})$ were equal to $\xi\hat{\beta}_{\bullet}$. This
last means that our scenarios consider the first reduction in the
effective transmission contact rates by NIPs. Using values in
\Cref{table_icparam,table_icparam2}, we build confidence intervals for
$\xi\hat{\beta}_{\bullet}$. These results are shown in
\Cref{table_icparam3}.
\begin{table}[h!]
\begin{center}
	\begin{tabular}{cc}
		\toprule
	    Parameter & 95\% Confidence Interval
			\\
			\midrule
            $\beta_S = \xi\hat{\beta}_S$ & $[0.2483712, 0.48720714]$ \\
            $\beta_A = \xi\hat{\beta}_A$ & $[0.1851696, 0.32181249]$ \\
			\bottomrule
	\end{tabular}
  \caption{Confidence interval for parameters
  $\beta_{\bullet}$.}\label{table_icparam3}
\end{center}
\end{table}
