\documentclass[3p, sort&compress]{elsarticle}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsbsy}
\usepackage{amstext}
\usepackage{amsfonts}
\usepackage{amstext}
\usepackage{mathrsfs}
\usepackage{graphpap}
\usepackage{graphics,graphicx}
\usepackage[utf8]{inputenc}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{array}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage[section]{placeins}
\usepackage{xargs}
\usepackage[pdftex,dvipsnames]{xcolor}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\graphicspath{{./plotly_chart_studio_figures/}}
\graphicspath{{./figures/}}
%
%
\newcommandx{\unsure}[2][1=]{%
    \todo[
        linecolor=red,
        backgroundcolor=red!25,
        bordercolor=red, #1]{#2}
}%
\newcommandx{\change}[2][1=]{%
    \todo[
        linecolor=blue,
        backgroundcolor=blue!25,
        bordercolor=blue, #1]{#2}
}
\newcommandx{\info}[2][1=]{%
    \todo[
        linecolor=OliveGreen,
        backgroundcolor=OliveGreen!25,
        bordercolor=OliveGreen, #1]{#2}
}
\newcommandx{\improvement}[2][1=]{
    \todo[linecolor=Plum,
        backgroundcolor=Plum!25,
        bordercolor=Plum,#1]{#2}
}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
\hypersetup{colorlinks = true, allcolors = blue}
\usepackage[nameinlink,noabbrev]{cleveref}
\newcommand{\R}{\mathbb{R}}
\newcommand{\e}{\varepsilon}
\newcommand{\f}{\mathfrak{F}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\newtheorem{teor}{Theorem}
\newtheorem{lemma}{Lemma}
\usepackage[toc,page]{appendix}
%
%
\begin{document}
    \begin{frontmatter}
        \title{
            Optimal vaccination preventive policies for COVID-19\\
        }
        \author[add:conacyt_unison]{%
            Sa\'ul D\'iaz-Infante%
            \corref{corresponding_author}%
        }%
        \ead{saul.diazinfante@unison.mx}
        \address[add:conacyt_unison]{
            CONACYT-Universidad de Sonora, Departamento de Matem\'aticas,
            Blvd. Luis Encinas y Rosales S/N,
            Hermosillo, Sonora, M\'exico, C.P. 83000.
        }
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \author[add:unison]%
        {Manuel Adrian Acu\~na-Zegarra}
        \ead{adrian.acuna@unison.mx}
        \address[add:unison]{
            Departamento de Matem\'aticas, Universidad de Sonora,
            Blvd. Luis Encinas y Rosales S/N,
            Hermosillo, Sonora, M\'exico, C.P. 83000.
        }
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \author[add:itson]%
            {David Baca-Carrasco}
            \ead{david.baca@itson.edu.mx}
        \address[add:itson]{
                Departamento de Matem\'aticas, Instituto Tecnol\'ogico de
                Sonora, 5 de Febrero 818 Sur, Colonia Centro, Ciudad
                Obregón,
                Sonora, M\'exico, C.P. 85000.
        }
        \author[add:unison]%
        {Daniel Olmos-Liceaga}
        \ead{daniel.olmos@unison.mx}
    \cortext[corresponding_author]{Corresponding author}
    \begin{keyword}
        Optimal Control, COVAX
        Vaccination, COVID-19.
    \end{keyword}
    \begin{abstract}
        BACKGROUND
        At the date, Europe and North America experiments the second wave of
        COVID-19 causing more than \num{1200000} deaths worldwide.
        Humanity lacks of successful treatment and the only plausible solution
        is an effective vaccine. Currently,four are in final phase three trials.
        If third stage trial results favorable, Pharmaceutics firms
        estimate big scale production of its vaccine candidates around
        first 2021  quarter.
        However, determine the vaccine efficacy, induced immunity response
        among other essential parameters still are under study and subject to
        uncertainty. In fact, is possible that
        first  vaccines will not be fully protective.
        Instead they may reduce the severity of illness, reducing
        hospitalization and death cases.
        Further, logistic supply, economical and political implications
        impose a set of great challenges to develop vaccination policies.
        PROBEM SETUP
        For this reason, health decision makers requires tools to evaluate
        hypothetical scenarios.
        FINDINGS
        Our contribution partially answers
        important modeling questions regarding to WHO Strategic
        Advisory Group of Experts (SAGE) on
        Immunization Working Group on COVID-19 Vaccines.

        Our results suggest that optimal control theory could be an option
        tool to develop  vaccination policies that satisfies important
        constrains as coverage horizon time supply restriction. We also report
        here simulation of vaccination polices with vaccine parameters reported
        by the most promising alternatives.

        COVID-19, which includes vaccination dynamics. We apply optimal control
        theory to propose optimal vaccine strategies that minimize DALYs.
        Additionally, we analyze the vaccination reproductive number around the
        basic reproductive number and the vaccination profile (coverage,
        efficacy,
        horizon time, and vaccination rate). Due to the uncertainty about the
        profile vaccine, our results explore some scenarios regarding efficacy,
        coverage, induced immunity by vaccination, and natural immunity. Here,
        we
        observe that: i) there are strategies that reduce DALYs and cumulative
        deaths at the horizon time compare to its counterpart with constant
        vaccination; ii) it is necessary information about vaccine efficacy to
        design optimal strategies, and iii) ...
    \end{abstract}
    \journal{Mathematical Biosciences}
\end{frontmatter}
%
    \section{Introduction}
        \input{introduction}
    \section{Mathematical model formulation}
        \input{model_formulation}
    \section{Model Analysis}
        %\textbf{[David]}
        \input{analysis}
    \section{Optimal Vaccination
    policies}
        \input{optimal_controll_modeling}
    \section{Numerical experiments}
        \input{numerical_experiments}
    \section{Conclusions and Discussions}
        \input{conclusions}
    \section*{Acknowledgement}
    The authors acknowledge support
    from grant DGAPA-PAPIIT IV100220
    and the Laboratorio Nacional de
    Visualización Científica UNAM.
    MAAZ acknowledges support from
    PRODEP Programme (No.
    511-6/2019-8291). DBC
    acknowledges support from PRODEP
    Programme (). We thank Jorge
    X. Velasco-Hernandez for its usefol comments and feedback.
    \section*{Author contributions}
    MAAZ .
    SDIV designed the study, provided oversight for all
    aspects of the study, developed the controlled modeling
    framework, developed simulation code for the BOCOP optimization,
    developed R-scripts for parameters calibration with Stan-R interface and
    wrote
    Sections 4 and 5 of the manuscript.
    DBC
    DOL
    \bibliographystyle{elsarticle-num-names}
    \bibliography{Vaccination_Bibliography}
    \begin{appendices}
        \section{Parameter estimation}
        \input{first_appendix}
    \end{appendices}
\end{document}
