---
 title: "Vaccination estimation Ciudad de Mexico"
 date: "`r Sys.Date()`"
 author: DIVS, DGS, FPA, GASV
 output:
     rmdformats::material:
        self_contained: true
        thumbnails: true
        lightbox: true
        gallery: false
        highlight: tango
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Baseline dynamics
=================================
\begin{align}
    S' & =
        \mu N^\star - (\lambda +  \mu) S
    \\
    E' & =
        \lambda S - (\kappa E + \mu E)
    \\
    I_S' & =
        p \kappa E - (\gamma_S +  \delta_H + \mu_{I_S} + \mu) I_S
    \\
    I_A' &=
        (1 - p) \kappa E - (\gamma_A + \mu) I_A
    \\
    H' &=
        \delta_H I_S - (\gamma_H + \mu_H +  \mu) H 
    \\
    R' & =
        \gamma_S I_S + \gamma_A I_A + \gamma_H H - \mu R
    \\
    D' &=
        \mu_{I_S} I_S + \mu_H H
    \\
    \lambda &:=
        \frac{\beta_A I_A + \beta_S I_S}{N^{\star}}
    \\
    N^{\star}(t) &=
        S + E + I_S + I_A +
        H + R
\end{align}

Stan ODE notation beginning model
=================================

|state                  |Stan| Initial Condition       |Stan     |Postulated |
|-----------------------|----|-------------------------|---------|-----------|
|$S$                    |y[1]| $S_0$                   |y_init[1]|$N -
                                                                  (I_{S_0} + 
                                                                  I_{A_0} 
                                                                  + E_0)$    |
|$E$                  |y[2]| $E_0$                   |y_init[2]|Unif(74, 2100)|
|$I_S$                |y[3]| $I_{s_0}$               |y_init[3]|22 (cdmx data)|
|$I_A$                |y[4]| $I_{a_0}$               |y_init[4]|Unif(74, 2100)|
|$H$                  |y[5]| $H_0$                   |y_init[5]|0          |
|$R$                  |y[6]| $R_0$                   |y_init[6]|0          |
|$D$                  |y[7]| $D_0$                   |y_init[7]|0          |
|$I_s^{[cumulative]}$ |y[8]| $I_{s_0}^{[cumulative]}$|y_init[8]|74 (cdmx data)|


Observation Model
=================
\begin{align}
    Y_t &
        \sim \text{Poisson}(\lambda_t), \qquad
    \\
    \lambda_t &
        =  \int_0^t \rho \delta_e E
    \\
    & p \sim \text{Uniform(0.3 0.8)}
    \\
    & \kappa: \sim \text{Gamma(10,50)}
\end{align}

March 10 -- March 30 parameters estimation
==========================================

|stan notation| symbol     |Prior          | Fixed      |
|-------------|---------   |---------------|------------|
|theta[1]     |$\beta_S$   | Normal(1, 0.3)|            |
|theta[2]     |$\beta_A$   | Normal(1, 0.3)|            |
|theta[3]     |$\kappa$    | Gamma(10, 100)|            |
|theta[4]     |$p$         | Unif(0.3, 0.8)|            |
|theta[5]     |$\delta_H$  | Gamma(10, 40) |            |
|theta[6]     |$\mu_{I_S}$ | Gamma(10, 80) |            |
|theta[7]     |$\mu_H$     | Gamma(10, 350)|            |
|theta[8]     |$\gamma_S$  | Gamma(10, 350)|            |
|theta[9]     |$\gamma_A$  | Gamma(10, 350)|            |
|theta[10]    |$\gamma_H$  | Gamma(10, 350)|            |
|y_init[2]    |$E_0$       | Unif(74, 2100)|            |
|y_init[3]    |$I_S$       | -----------   |22          |
|y_init[4]    |$I_A$       | Unif(74, 2100)|            |


Postulated densities
=====================
```{r, include=TRUE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(plotly)
library(rstan)
mu_ <- function(lambda, ylabel= "mu_h"){
    # We suppose mu_. as a exponential r.v.
    x <- seq(from = 0, to = 1, by=.001)
    mu_h_ <- dexp(x, rate = lambda)
    df <- data.frame(x=x, mu_h = mu_h_)
    mean_ <- 1/lambda
    mean_time <- 1/mean_ 
    text <- paste(mean_time,"days")
        p <- ggplot(data=df,
                aes(x = x,
                    y = mu_h)) + 
        xlab("x")+
        ylab(ylabel) +
        geom_line(colour = "#000000") +
        geom_area(alpha = 0.6, fill = "lightgray") + 
        geom_vline(xintercept = mean_, linetype="dotted", 
                color = "red", size=0.5)+
        annotate(geom = "text", x = 1.30 * mean_, y=0, label = text,
              color="black")
    return(p)
}
#
gamma_ <- function(alpha, beta, ylabel="gamma_S"){
    # We suppose mu_. as a exponential r.v.
    theta <- 1 / beta 
    x <- seq(from = 0, to = 1, by=.001)
    gamma_s_ <- dgamma(x, shape = alpha, 
                        scale= theta)
    df <- data.frame(x=x, gamma_s = gamma_s_)
    mean_ <- alpha * theta
    mean_time <- 1/mean_ 
    text <- paste(mean_time,"days")
    p <- ggplot(data=df,
                aes(x = x,
                    y = gamma_s)) + 
        geom_line(colour = "#000000") +
        geom_area(alpha = 0.6, fill = "lightgray") +
        geom_vline(xintercept = mean_, linetype="dotted", 
                color = "red", size=0.5) + 
        annotate(geom="text", x=1.30 * mean_, y=0, label = text,
              color="black")
        return(p)
}
pi_mu_h <- mu_(lambda = 25, ylabel= "mu_h")
pi_mu_i_s <- mu_(lambda = 35, ylabel= "mu_i_s")
pi_gamma_s <- gamma_(alpha = 10, beta = 100,  ylabel= "gamma_S")
pi_gamma_a <- gamma_(alpha = 10, beta = 50,  ylabel= "gamma_A")
pi_gamma_h <- gamma_(alpha = 10, beta = 250,  ylabel= "gamma_H")

fig6 <- ggplotly(pi_mu_h)
fig7 <- ggplotly(pi_mu_i_s)
fig8 <- ggplotly(pi_gamma_s)
fig9 <- ggplotly(pi_gamma_a)
fig10 <- ggplotly(pi_gamma_h)
fig6
fig7
fig8
fig9
fig10

```

Stan estimation
===============================
```{r}
library(knitr)
library(kableExtra)
#
#
sub_path_1 <- "/home/saul/sauld@cimat.mx/UNISON/Articles/NovelCovid-19"
sub_path_2 <- "NovelCovid19-ControlModelling"
sub_path_3 <- "NovelCovid19-ControlModellingGitHub"
sub_path_4 <- "UNISON-UADY-VACCINATION-PRJ/r_sources"
sub_path_5 <- "mcmc_parameter_estimation/estimation"
file_name <- "last_est.csv"
path <- paste(sub_path_1, 
                sub_path_2, 
                sub_path_3, 
                sub_path_4,
                sub_path_5,
                file_name, 
                sep = "/")
parameters_df <- read.csv(path, header=FALSE, skip = 1)
parameters_df <- data.frame(parameters_df)
#
colnames(parameters_df) <- c("theta",
                        "mean", 
                        'se_mean',
                        'sd',
                        '2.5%', '25%','50%', '75%' ,'97.5%',
                        'n_eff',
                        'Rhat')
kable(parameters_df)  %>%
  kable_styling(bootstrap_options = "striped", full_width = T)

```


Lockdown-Vaccination-Treatment-Model
====================================
\begin{align}
    S'(t) &=
        \mu \bar{N}
        -\frac{\beta_S I_S+\beta_AI_A}{\bar{N}}S
        -(\mu+\lambda_V)S +\delta_V V
    \\
    E'(t) &=
        \frac{\beta_S I_S
        + \beta_A I_A}{\bar{N}} S
        + \epsilon \frac{\beta_S I_S + \beta_A I_A}{\bar{N}}V
        - (\mu+\delta_E) E \nonumber
    \\
    I'_S(t) & =
        p \delta_E E
        -(\mu + \mu_S + \alpha_S + \lambda_T) I_S
        +(1 - q) \alpha_T T
    \\
    I'_A(t) & =
        (1-p) \delta_E E
        - (\mu + \mu_A + \alpha_A) I_A
    \\
    R'(t) & =
        \alpha_S I_S
        + \alpha_A I_A
        + q \alpha_T T
        - \mu R
    \\
    D'(t)& =
        \mu_S I_S
        + \mu_A I_A
    \\
    V'(t)& =
        \lambda_V S
        - \epsilon
        \frac{\beta_S I_S + \beta_A I_A}{\bar{N}} V
        - (\mu + \delta_V) V
    \\
    T'(t) &=
        \lambda_T I_S
        -(\mu + \alpha_T) T
    \\
    \bar{N}(t) &=
        S(t) + E(t) + I_S(t) + I_A(t) + R(t) + V(t) + T(t)
\end{align}

Model from March 24 July 14
===========================

|state                  |Stan | Initial Condition       |Stan      |Postulated |
|-----------------------|-----|-------------------------|----------|-----------|
|$S$                    |y[1] | $S_0$                   | y_init[1]|$N -
                                                    (I_{S_0} + I_{A_0} + E_0)$|
|$E$                    |y[2] | $E_0$                   | y_init[2]|Unif(0, 10)|
|$I_s$                  |y[3] | $I_{s_0}$               | y_init[3]|Unif(0, 3) |
|$I_a$                  |y[4] | $I_{a_0}$               | y_init[4]|Unif(0, 10)|
|$R$                    |y[5] | $R_0$                   | y_init[5]|Estimated  |
|$T$                    |y[5] | $R_0$                   | y_init[5]|0          |
|$V$                    |y[5] | $R_0$                   | y_init[5]|0          |
|$I_s^{[cumulative]}$   |y[6] | $I_{s_0}^{[cumulative]}$| y_init[6]|$I_{s_0}$  |


    
```{r}
seirvt_mod = function(t, state, parameters){
    with(as.list(c(state, parameters)), {
    ####
    n_bar <- s + e + i_s + i_a + r + v + treat
    force_infection = (beta_s * i_s + beta_a * i_a) / n_bar
    rhs_s = mu * n_bar - force_infection * s - (mu + lambda_v) * s + delta_v * v
    rhs_e = force_infection * (epsilon * v + s) - (mu + delta_e) * e
    rhs_i_s = p * delta_e * e - (mu + mu_s + alpha_s + lambda_t) * i_s -
        (1.0 - q) * alpha_t * treat
    rhs_i_a = (1 - p) * delta_e * e - (mu + mu_a + alpha_a) * i_a
    rhs_r = alpha_s * i_s + alpha_a * i_a + q * alpha_t * treat - mu * r
    rhs_d = mu_s * i_s + mu_a * i_a
    rhs_v = lambda_v * s - epsilon * force_infection * v - (mu + delta_v) * v
    rhs_treat = lambda_t * i_s - (mu + alpha_t) * treat
    rhs = c(rhs_s, rhs_e, rhs_i_s, rhs_i_a, rhs_r, rhs_d, rhs_v, rhs_treat)
    return(list(rhs))
    })
}
```

March 24 --Jun 01 parameters estimation
=======================================

|stan notation | symbol     |Prior            | Fixed      |
|--------------|---------   |---------------  |------------|
|theta[1]      |$\beta_A$   | Normal(1, 0.3)  |            |
|theta[2]      |$\beta_S$   | Normal(1, 0.3)  |            |
|theta[3]      |$p$         | Unif(.3, 0.8)   |            |
|theta[3]      |$q$         | Unif(0.4, 0.7)  |            |
|theta[4]      |$\epsilon$  |                 |0.0         |
|theta[5]      |$\alpha_S$  | Gamma(10, 100)  |            |
|theta[6]      |$\alpha_A$  | Gamma(10, 50)   |            |
|theta[7]      |$\alpha_T$  |                 |0.0         |
|theta[8]      |$\lambda_V$ |                 |0.0         |
|theta[9]      |$\lambda_T$ |                 |0.0         |
|theta[10]     |$\mu_S$     |                 |            |
|---------     |$\mu_A$     |                 |0.0         |
|---------     |$\mu$       | --------        |3.913894e-05|
|theta[11]     |$\delta_V$  |                 |0.0         |
|theta[12]     |$\delta_E$  | Gamma(10, 50)   |0.1960784   |
|---------     |$E_0$       | Unif(0, 10)     |            |
|---------     |$I_A$       | Unif(0, 10)     |            |
|---------     |$I_S$       | Unif(0, 10)     |            |
|---------     |$I_A$       | Unif(0, 10)     |            |

Stan ODE notation
==========================
|variable               | Stan| Initial Condition       |Stan      |           |
|--------               |-----|------------------       | ---------|------     |
|$S$                    |y[1] | $S_0$                   | y_init[1]|$N -
                                                                     (I{s_0} +
                                                                     I_{a_0} +
                                                                     E_0)$     |
|$E$                    |y[2] | $E_0$                   | y_init[2]|Unif(0, 10)|
|$I_s$                  |y[3] | $I_{s_0}$               | y_init[3]|Unif(0, 3) |
|$I_a$                  |y[4] | $I_{a_0}$               | y_init[4]|Unif(0, 10)|
|$R$                    |y[5] | $R_0$                   | y_init[5]|0          |
|$D$                    |y[6] | $D_0$                   | y_init[6]|0          |
|$V$                    |y[7] | $V_0$                   | y_init[7]|0          |
|$T$                    |y[8] | $V_0$                   | y_init[8]|0          |
|$I_s^{[cumulative]}$   |y[9] | $I_{s_0}^{[cumulative]}$| y_init[9]|$I_{s_0}$  |

Stan MODEL
===============================
```{r}
library(rstan)
writeLines(readLines("seirh.stan"))
```

Observation Model
=================
\begin{align}
    Y_t &
        \sim \text{Poisson}(\lambda_t), \qquad
    \\
    \lambda_t &
        =  \int_0^t p \kappa E
    \\
    & p \sim \text{Uniform(0.3 0.8)}
    \\
    & \kappa \sim \text{Gamma(10, 52)}
\end{align}
